### 2023-02-20 Conference Submission/DraftDoc.tex
started edits to methodology

\begin{section}{Methodology}
    We used a singular value decomposition of each matrix to embed our network in a low dimensional space.\
        \[
        A = U\Sigma V'
        \]
    Where $\Sigma_{ii} = \sigma_i$ and $\sigma_i > sigma_{i+1}$ and each $\sigma_i$ is a non-negative square root of the matrices $AA', \space A'A$. $U$ is a matrix made from the orthonormalised eigenvectors of $AA'$ associated with $\sigma_i$, and $V$ is a matrix made from the orthonormalised eigenvectors of $A'A$ associated with $\sigma_i$. Each row $i$ of $U$ and $V$ represents the in and out position of node $i$ respectively. This can be truncated at an arbitrary number of eigenpairs to form a low dimentional approximation to $A$.
        \[
        A \approx \hat U \hat \Sigma \hat V'
        \]\\
    Where $\hat U, \hat \Sigma, \hat V$ are the first $d$ columns of $U, \Sigma, V$ \cite{golub1971singular}. $\hat U \sqrt{\hat \Sigma}$ is still associated with the in edges of our nodes, and $\sqrt{\hat \Sigma} \hat V' $ is still associated with the out edges of our nodes, but now we have simplified our system whilst keeping as much information as possible due to our descending order of singular values. These two matrices form our $d$ dimensional embedding.\\

>>>>

\begin{section}{Methodology}

    XXX A couple of rows about RDPG XXX

    XXX what are these matrix XXX

    We used a Singular Value Decomposition of each matrix to embed our network in a low dimensional space.\
        \[
        A = U\Sigma V'
        \]
    XXX Let's not explain SVD, at most give a ref XXX
    This can be truncated at an arbitrary number of eigenpairs to form a low dimentional approximation to $A$.
        \[
        A \approx \hat U \hat \Sigma \hat V'
        \]\\
    Where $\hat U, \hat \Sigma, \hat V$ are the first $d$ columns of $U, \Sigma, V$ \cite{golub1971singular}. $\hat U \sqrt{\hat \Sigma}$ is still associated with the in edges of our nodes, and $\sqrt{\hat \Sigma} \hat V' $ is still associated with the out edges of our nodes, but now we have simplified our system whilst keeping as much information as possible due to our descending order of singular values. These two matrices form our $d$ dimensional embedding.\\
